URG analysis of the extended Kondo model with d-wave interaction

### 2024-02-01 dWaveESIAM.tex
--no-message

The off-diagonal part of the Hamiltonian on the other hand leads to scattering in the states \(\left\{ \vec q \right\} \):
\begin{equation}\begin{aligned}
	H_X^{(j)} =& \underbrace{\sum_{\vec k, \vec q, \sigma,\sigma^\prime}J_{\vec k, \vec q} \vec{S}_d\cdot\vec{\tau}_{\sigma,\sigma^\prime}\left[c^\dagger_{\vec q\sigma}c_{\vec k,\sigma} + \text{h.c.}\right]}_{T_1^\dagger + T_1} \\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec k_3, \vec k_4,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec k_4} \sigma\sigma^\prime \left[c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec k_4,\sigma^\prime} + \text{h.c.}\right]}_{T_2^\dagger + T_2}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec q_2, \vec k_4,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime \left[c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} + \text{h.c.}\right]}_{T_3^\dagger + T_3}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2,\vec k_3,\vec q_2,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec q_2} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec q_2,\sigma^\prime}}_{T_4}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2,\vec k_3,\vec q_2,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec q_2} \sigma\sigma^\prime c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec q_2,\sigma^\prime}c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}}_{T_5}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec q_2, \vec q_3,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2, \vec q_2, \vec q_3} \sigma\sigma^\prime \left[c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec q_3,\sigma^\prime}c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma} + \text{h.c.}\right]}_{T_6^\dagger + T_6}~,\\
		   & \underbrace{+\sum_{\vec k, \vec q, \sigma,\sigma^\prime}J_{\vec q^\prime, \vec q} \vec{S}_d\cdot\vec{\tau}_{\sigma,\sigma^\prime}\left[c^\dagger_{\vec q\sigma}c_{\vec q^\prime,\sigma}\right]}_{T_7}~.\\
\end{aligned}\end{equation}
The first term \(T_1\) is an impurity-mediated scattering between the states \(\vec q\) at energy \(\varepsilon_j\) and the states \(\vec k\) at energies below \(\varepsilon_j\). Terms \(T_2\) through \(T_6\) involve two-particle scattering between these momentum states involving an increasing number of participating states from the isoenergetic shell \(\varepsilon_j\), through the Hubbard-like local term \(W\). The renormalisation of the Hamiltonian is constructed from the general expression
\begin{equation}\begin{aligned}
	\Delta H^{(j)} = H_X \frac{1}{\omega- H_D} H_X~.
\end{aligned}\end{equation}

@@

Next, we consider scattering processes involving \(T_6\):
\begin{equation}\begin{aligned}
	T_{1,z}^\dagger G T_6 = \frac{1}{4}\sum_{\vec k_1,\vec k_2,\vec q,\sigma}\sigma J_{\vec k_2,\vec q}S_d^z c^\dagger_{\vec q,\sigma} c_{\vec k_2,\sigma} \frac{1}{\omega - H_D}W_{\vec q,\vec q,\vec q,\vec k_1} \left[-c^\dagger_{\vec k_1,\sigma}c_{\vec q,\sigma}\hat n_{\vec q,\bar\sigma} + c^\dagger_{\vec k_1,\sigma}c_{\vec q,\sigma}\hat n_{\vec q,\sigma} + c^\dagger_{\vec k_1,\sigma}\left(1 - \hat n_{-\vec q,\sigma}\right) c_{\vec q,\sigma}\right]~.
\end{aligned}\end{equation}
For the same reasons as those outlined above eq.~\ref{t2t61}, the first two terms on the right-hand side of the Greens function cancel each other. The remaining term evaluates to
\begin{equation}\begin{aligned}
	T_{1,z}^\dagger G T_6 = \frac{1}{4}\sum_{\vec k_1,\vec k_2,\sigma}\sigma  S_d^z c_{\vec k_2,\sigma}c^\dagger_{\vec k_1,\sigma} \sum_{\vec q\in\text{PS}}\frac{J_{\vec k_2,\vec q} W_{\vec q,\vec q,\vec q,\vec k_1}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2} = -\frac{1}{4}\sum_{\vec k_1,\vec k_2,\sigma} S_d^z \sigma c^\dagger_{\vec k_1,\sigma} c_{\vec k_2,\sigma} \sum_{\vec q\in\text{PS}}\frac{J_{\vec k_2,\vec q} W_{\vec q,\vec q,\vec q,\vec k_1}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2}~.
\end{aligned}\end{equation}
Another scattering process is obtained by switching the operators \(T_1\) and \(T_6\):
\begin{equation}\begin{aligned}
	T_{6}^\dagger G T_{1,z} &= \frac{1}{4} \sum_{\vec k_1,\vec k_2,\vec q,\sigma} \left[-c^\dagger_{\vec q,\sigma_1}c_{\vec k_2,\sigma_1}\hat n_{-\vec q,\bar\sigma_1} + c^\dagger_{\vec q,\sigma_1}c_{\vec k_2,\sigma_1}\hat n_{-\vec q,\sigma_1} + c^\dagger_{\vec q,\sigma_1}\left(1 - \hat n_{-\vec q,\sigma_1}\right) c_{\vec k_2,\sigma_1}\right] \frac{W_{\vec q,\vec q,\vec q,\vec k_2} J_{\vec k_1,\vec q}}{\omega - H_D} \sigma S_d^z c^\dagger_{\vec k_1,\sigma} c_{\vec q,\sigma}\\
				&=-\frac{1}{4}\sum_{\vec k_1,\vec k_2,\sigma} S_d^z \sigma c^\dagger_{\vec k_1,\sigma} c_{\vec k_2,\sigma} \sum_{\vec q\in\text{PS}}\frac{J_{\vec k_1,\vec q} W_{\vec q,\vec q,\vec q,\vec k_2}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2}
\end{aligned}\end{equation}
One can also construct

>>>>

The off-diagonal part of the Hamiltonian on the other hand leads to scattering in the states \(\left\{ \vec q \right\} \):
\begin{equation}\begin{aligned}
	H_X^{(j)} =& \underbrace{\sum_{\vec k, \vec q, \sigma,\sigma^\prime}J_{\vec k, \vec q} \vec{S}_d\cdot\vec{\tau}_{\sigma,\sigma^\prime}\left[c^\dagger_{\vec q\sigma}c_{\vec k,\sigma} + \text{h.c.}\right]}_{T_1^\dagger + T_1} \\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec k_3, \vec k_4,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec k_4} \sigma\sigma^\prime \left[c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec k_4,\sigma^\prime} + \text{h.c.}\right]}_{T_2^\dagger + T_2}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec q_2, \vec k_4,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime \left[c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} + \text{h.c.}\right]}_{T_3^\dagger + T_3}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2,\vec k_3,\vec q_2,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec q_2} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec q_2,\sigma^\prime}}_{T_4}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2,\vec k_3,\vec q_2,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec q_2} \sigma\sigma^\prime c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec q_2,\sigma^\prime}c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}}_{T_5}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec q_2, \vec q_3,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2, \vec q_2, \vec q_3} \sigma\sigma^\prime \left[c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec q_3,\sigma^\prime}c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma} + \text{h.c.}\right]}_{T_6^\dagger + T_6}~,\\
\end{aligned}\end{equation}
The first term \(T_1\) is an impurity-mediated scattering between the states \(\vec q\) at energy \(\varepsilon_j\) and the states \(\vec k\) at energies below \(\varepsilon_j\). Terms \(T_2\) through \(T_6\) involve two-particle scattering between these momentum states involving an increasing number of participating states from the isoenergetic shell \(\varepsilon_j\), through the Hubbard-like local term \(W\). The renormalisation of the Hamiltonian is constructed from the general expression
\begin{equation}\begin{aligned}
	\Delta H^{(j)} = H_X \frac{1}{\omega- H_D} H_X~.
\end{aligned}\end{equation}

@@

Next, we consider scattering processes involving \(T_6\):
\begin{equation}\begin{aligned}
	T_{1,z}^\dagger G T_6 = \frac{1}{4}\sum_{\vec k_1,\vec q,\sigma}\sigma J_{\vec k_2,\vec q}S_d^z c^\dagger_{\vec q,\sigma} c_{\vec k_2,\sigma} \frac{1}{\omega - H_D} W_{\vec q,\vec q,\vec q,\vec k_1} \left(-c^\dagger_{k_1\sigma}c_{q\sigma}\hat n_{\vec q\sigma} - \hat n_{\vec q\sigma} c^\dagger_{k_1\sigma}c_{q\sigma} + 2 c^\dagger_{k_1\sigma}c_{q\sigma}\hat n_{\vec q\bar\sigma} + 2\hat n_{\vec q\bar\sigma} c^\dagger_{k_1\sigma}c_{q\sigma}\right)~.
\end{aligned}\end{equation}
For the same reasons as those outlined above eq.~\ref{t2t61}, the first three terms on the right-hand side of the Greens function cancel each other. The remaining term evaluates to
\begin{equation}\begin{aligned}
	T_{1,z}^\dagger G T_6 = \frac{1}{2}\sum_{\vec k_1,\vec k_2,\sigma}\sigma S_d^z c_{\vec k_2,\sigma}c^\dagger_{\vec k_1,\sigma} \sum_{\vec q\in\text{PS}}\frac{J_{\vec k_2,\vec q} W_{\vec q,\vec q,\vec q,\vec k_1}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2} = -\frac{1}{2}\sum_{\vec k_1,\vec k_2,\sigma} S_d^z \sigma c^\dagger_{\vec k_1,\sigma} c_{\vec k_2,\sigma} \sum_{\vec q\in\text{PS}}\frac{J_{\vec k_2,\vec q} W_{\vec q,\vec q,\vec q,\vec k_1}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2}~.
\end{aligned}\end{equation}
Another scattering process is obtained by switching the operators \(T_1\) and \(T_6\):
\begin{equation}\begin{aligned}
	T_{6}^\dagger G T_{1,z} &= \frac{1}{4} \sum_{\vec k_1,\vec k_2,\vec q,\sigma} \left(2\hat n_{\vec q\bar\sigma} c^\dagger_{q\sigma}c_{k_2\sigma}\right) \frac{W_{\vec q,\vec q,\vec q,\vec k_2} J_{\vec k_1,\vec q}}{\omega - H_D} \sigma S_d^z c^\dagger_{\vec k_1,\sigma} c_{\vec q,\sigma} = -\frac{1}{2}\sum_{\vec k_1,\vec k_2,\sigma} S_d^z \sigma c^\dagger_{\vec k_1,\sigma} c_{\vec k_2,\sigma} \sum_{\vec q\in\text{PS}}\frac{J_{\vec k_2,\vec q} W_{\vec q,\vec q,\vec q,\vec k_1}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2}
\end{aligned}\end{equation}
One can also construct the particle-hole exchanged processes:
\begin{equation}\begin{aligned}
	T_6 G T_{1,z}^\dagger = \frac{1}{4}\sum_{\vec k_1, \vec k_2, \vec q, \sigma}\left(-c^\dagger_{k_1\sigma}c_{q\sigma}\hat n_{\vec q\sigma} - \hat n_{\vec q\sigma} c^\dagger_{k_1\sigma}c_{q\sigma} + 2 c^\dagger_{k_1\sigma}c_{q\sigma}\hat n_{\vec q\bar\sigma} + 2\hat n_{\vec q\bar\sigma} c^\dagger_{k_1\sigma}c_{q\sigma}\right) \frac{J_{\vec k_2,\vec q} W_{\vec q,\vec q,\vec q,\vec k_1}}{\omega - H_D} \sigma S_d^z c^\dagger_{\vec q,\sigma} c_{\vec k_2,\sigma} = ~.
\end{aligned}\end{equation}
